### 2019-06-08 2-Chapters/4-Chapter/IEEE_WCNC_2019__DemoICT.git/main.tex
Done for proof reading chapter 4

\paragraph{Related works.}
% \TODOL{Est-ce que je fais ça ici ou à la fin du chapitre 5 ? Ou peut-être en chapitre 1, ça ferait du contenu au chapitre 1...}
%
We evoke quickly here some previous works that similarly implemented proof-of-concepts to show that reinforcement learning algorithms can be used within real-world wireless communications.
Starting from $2010$, the works of Wassim Jouini \cite{Jouini09,Jouini10,Jouini12} were the first ones to propose to use Reinforcement Learning for Cognitive Radio, especially MAB and the \UCB{} algorithm, and from $2014$, proof-of-concepts were developed by Christophe Moy and his student Clément Robert \cite{RobertSDR2014,MoyWSR2014}.
In $2015$ and $2016$, Christophe Moy continued to work on this direction, with a PhD student (Navikkumar Modi) and post-doc (Sumit J. Darak) in our team SCEE, for the following publications
\cite{darak2016bayesian,Darak16,modiDemo2016,kumar2016two}.
Since $2017$, Sumit J. Darak and his team at IIIT Delhi have been very active in the research on cognitive radio using multi-armed bandits, and some of their recent works are illustrated with real-world demo using USRP and the MATLAB/Simulink system
\cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}.

@@

\paragraph{Physical layer and protocol.}

We implement a simple PHY/MAC layers solution, in order to demonstrate the possibility of improvement of the performance of IoT communications in unlicensed bands. We could have used any physical layer and any ALOHA-based protocol.
We choose to implement our own physical layer and protocol, for both clarity and conciseness, and because developing a complete IoT network protocol stack is no more a research work and would have fall outside of the scope of this thesis.

@@

The boards have their own power supply, and are all connected to a local Ethernet switch, itself connected to a single laptop, running GNU/Linux and Ubuntu.
The pictures in Figure~\ref{fig:42:photosSCEETestBed} shows the testbed used for these experiments.
% Octoclock
To ease the synchronization implementation in both time and frequency between the boards representing the dynamic devices and the gateway, we use an Octoclock \cite{OctoclockProduct}, also a product of Ettus Research,
% https://www.ettus.com/product/details/OctoClock-G
and coaxial cables connecting every platform to the Octoclock for time (PPS) and frequency synchronization, but this is not mandatory.

@@

\paragraph{Availability of data and materials.}
%
The source code of our demonstration is fully available online, open-sourced under GPLv3 license, at
\href{https://bitbucket.org/scee_ietr/malin-multi-arm-bandit-learning-for-iot-networks-with-grc}{\texttt{bitbucket.org/scee\_ietr/\\malin-multi-arm-bandit-learning-for-iot-networks-with-grc/}}.
%
It contains both the GNU Radio Companion flowcharts and blocks, with ready-to-use \texttt{Makefiles} to easily compile, install and launch the demonstration.
The demonstration only requires a laptop and free tools,
as the laptop should run a GNU/Linux distribution (like Ubuntu or Debian),
in addition to USRP platforms from Ettus Research.

@@

\paragraph{Video.}
%
As depicted in Figure~\ref{fig:42:screenshotDemoYouTube} above,
we realized a $6$-minute \textbf{video} to sum-up our demonstration and advertise our work online, and it is available on the YouTube hosting platform, at \texttt{\href{https://youtu.be/HospLNQhcMk}{youtu.be/HospLNQhcMk}}.
The video shows examples of $3$ dynamic devices learning simultaneously, confirming the results of Figure~\ref{fig:42:plot_datafile_append_Uniform_vs_UCB_vs_TS} for overlapping channels.
It also shows the connections between the USRP boards, the Octoclock, the master laptop etc, completing the presentation of the SCEE testbed already shown in Figure~\ref{fig:42:photosSCEETestBed}.
% \textcolor{white}{Of course, the video was not seen much, because our work is useless! Yay!}

>>>>

\textbf{Related works.}
% \TODOL{Est-ce que je fais ça ici ou à la fin du chapitre 5 ? Ou peut-être en chapitre 1, ça ferait du contenu au chapitre 1...}
%
We evoke here some previous works that similarly implemented proof-of-concepts to show that reinforcement learning algorithms can be used within real-world wireless communications.
Starting from $2010$, the works of Wassim Jouini \cite{Jouini09,Jouini10,Jouini12} were the first ones to propose to use Reinforcement Learning for Cognitive Radio, especially MAB and the \UCB{} algorithm, and from $2014$, proof-of-concepts were developed by Christophe Moy and his student Clément Robert \cite{RobertSDR2014,MoyWSR2014}.
In $2015$ and $2016$, Christophe Moy continued to work on this direction, with a PhD student (Navikkumar Modi) and post-doc (Sumit J. Darak) in our team SCEE, for the following publications
\cite{darak2016bayesian,Darak16,modiDemo2016,kumar2016two}.
Since $2017$, Sumit J. Darak and his team at IIIT Delhi have been very active in the research on cognitive radio using multi-armed bandits, and some of their recent works are illustrated with real-world demo using USRP and the MATLAB/Simulink system
\cite{KumarYadav2018,SawantKumar2018,JoshiKumar2018}.

@@

\textbf{Physical layer and protocol.}
%
We implement a simple PHY/MAC layers solution, in order to demonstrate the possibility of improvement of the performance of IoT communications in unlicensed bands. We could have used any physical layer and any ALOHA-based protocol.
We choose to implement our own physical layer and protocol, for both clarity and conciseness, and because developing a complete IoT network protocol stack is no more a research work and would have fall outside of the scope of this thesis.

@@

The boards have their own power supply, and are all connected to a local Ethernet switch, itself connected to a single laptop, running GNU/Linux and Ubuntu.
The pictures in Figure~\ref{fig:42:photosSCEETestBed} shows the testbed used for these experiments.
% Octoclock
To ease the synchronization in both time and frequency between the boards representing the dynamic devices and the gateway, we use an Octoclock \cite{OctoclockProduct}, also a product of Ettus Research,
% https://www.ettus.com/product/details/OctoClock-G
and coaxial cables connecting every platform to the Octoclock for time (PPS) and frequency synchronization, but this is not mandatory.

@@

\paragraph{Availability of data and materials.}
%
The source code of our demonstration is fully available online, open-sourced under GPLv3 license, at
\href{https://bitbucket.org/scee_ietr/malin-multi-arm-bandit-learning-for-iot-networks-with-grc}{\texttt{bitbucket.org/scee\_ietr/malin-multi-arm\\-bandit-learning-for-iot-networks-with-grc/}}.
%
It contains both the GNU Radio Companion flowcharts and blocks, with ready-to-use \texttt{Makefiles} to easily compile, install and launch the demonstration.
The demonstration only requires a laptop and open-source free softwares,
as the laptop should run a GNU/Linux distribution (like Ubuntu or Debian),
in addition to USRP platforms from Ettus Research.

\paragraph{Video.}
%
As depicted in Figure~\ref{fig:42:screenshotDemoYouTube} below,
we realized a $6$-minute \textbf{video} to sum-up our demonstration and advertise our work online, and it is available on the YouTube hosting platform, at \texttt{\href{https://youtu.be/HospLNQhcMk}{youtu.be/HospLNQhcMk}}.
The video shows examples of $3$ dynamic devices learning simultaneously, confirming the results of Figure~\ref{fig:42:plot_datafile_append_Uniform_vs_UCB_vs_TS} for overlapping channels.
It also shows the connections between the USRP boards, the Octoclock, the master laptop etc, completing the presentation of the SCEE testbed already shown in Figure~\ref{fig:42:photosSCEETestBed}.
% \textcolor{white}{Of course, the video was not seen much, because our work is useless! Yay!}

@@
